\documentclass[a4paper, twoside]{report}

%% Language and font encodings
\usepackage[english]{babel}
\usepackage[superscript,biblabel]{cite} %% Small superscript references
\usepackage[utf8x]{inputenc}
\usepackage[T1]{fontenc}

%% Sets page size and margins
\usepackage[a4paper,top=3cm,bottom=2cm,left=3cm,right=3cm,marginparwidth=1.75cm]{geometry}

%% Useful packages
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage[colorinlistoftodos]{todonotes}
\usepackage[colorlinks=true, allcolors=blue]{hyperref}

%% Technical drawing package
\usepackage{tikz}
\usetikzlibrary{arrows,chains,matrix,positioning,scopes,decorations.pathmorphing}

%% Math commands for formatting
\newcommand{\matr}[1]{\mathbf{#1}}
\DeclareMathOperator{\diag}{diag}

\title{Directing Wave Propagation by Topological Perturbation in Metamaterials
       [INTERIM REPORT]}
\author{Bernard Ting}

\begin{document}
\input{title/title.tex}

\begin{abstract}
We first introduce the theory of dispersion curves and plot them for simple
models. We then break the symmetry by introducing masses of different weights
and observe how this affects the dispersion curves. We then investigate these
structures in the case of media composed of one symmetry breaking ribbon above
another. We use this to find special frequencies or modes which are present in
the band gap. Scattering simulations are run with these frequencies induced to
the lattice to confirm our analysis.
\end{abstract}

\renewcommand{\abstractname}{Acknowledgements}
\begin{abstract}
I would like to extend my greatest thanks to my supervisor, Prof. Richard
Craster, for his advice and guidance on all matters relating to the project. I
would also like to thank Dr. Christopher Ford for being my second marker and
providing timely feedback regarding my project.
\end{abstract}

\tableofcontents
%% \listoffigures
%% \listoftables

\input{introduction/introduction.tex}
\input{background/background.tex}
\input{project/dispersion.tex}
\input{interim/project_plan.tex}
\input{interim/evaluation_plan.tex}

\bibliographystyle{unsrt}
\bibliography{bibs/bibliography}

\end{document}
