\documentclass[a4paper, twoside]{report}

%% Language and font encodings
\usepackage[english]{babel}
\usepackage[superscript,biblabel]{cite} %% Small superscript references
\usepackage[utf8x]{inputenc}
\usepackage[T1]{fontenc}

%% Sets page size and margins
\usepackage[a4paper,top=3cm,bottom=2cm,left=3cm,right=3cm,marginparwidth=1.75cm]{geometry}

%% Useful packages
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{subcaption}
\usepackage[colorinlistoftodos]{todonotes}
\usepackage[colorlinks=true, allcolors=blue]{hyperref}

%% Technical drawing package
\usepackage{tikz}
\usetikzlibrary{arrows,chains,matrix,positioning,scopes,decorations.pathmorphing,math}

%% Math commands for formatting
\newcommand{\matr}[1]{\mathbf{#1}}
\DeclareMathOperator{\diag}{diag}

\title{Emulating the Quantum Valley Hall Effect in Topologically Perturbed Model Systems}
\author{Bernard Ting}

\begin{document}
\input{title/title.tex}

\begin{abstract}
We investigate how the topological pertubation of an elastic mass-spring system
leads to the formation of bandgaps which behave similarly to the quantum
valley-Hall effect. We first introduce the theory of dispersion curves and plot
them for simple models. We then break the symmetry by introducing masses of
different weights and observe induces a bandgap. The resulting structures
composed of two media with different topological invariants have non-trivial
bandgaps which support edge waves at the interface. We analyse the dispersion
relations on the unit cell and finite strip to find special frequencies or
modes which are present in the band gap. Numerical scattering simulations are
then run with these frequencies induced to the lattice to confirm our analysis.
This work proposes several different ways of topologically perturbing lattices
as well as seek to show that this simple model is able to emulate the
behaviours and effects seen in more complex systems.
\end{abstract}

\renewcommand{\abstractname}{Acknowledgements}
\begin{abstract}
I would like to extend my greatest thanks to my supervisor, Prof. Richard
Craster, for his advice and guidance on all matters relating to the project. I
would also like to thank Dr. Christopher Ford for being my second marker and
providing timely feedback regarding my project.
\end{abstract}

\tableofcontents
%% \listoffigures
%% \listoftables

\input{introduction/introduction.tex}
\input{background/background.tex}
\input{project/dispersion.tex}
\input{project/perturbed.tex}
\input{project/scattering.tex}
\input{project/complexbends.tex}
\input{evaluation/evaluation.tex}
\input{conclusion/conclusion.tex}

\bibliographystyle{unsrt}
\bibliography{bibs/bibliography}

\end{document}
