\chapter{Project plan}

\section{What has been done}

\subsection{Report}
\begin{itemize}
  \item Thought about the structure as a whole, and arranged
        chapters/subchapters into an order which (I think) flows naturally and
        smoothly.
  \item Most of the core points of Introduction and Background. However, I
        think that I can still expand much more on the points already
        mentioned.
  \item Started discussion of basic models to form the basis of intuition for
        the more complex model which our project revolves around. Done with 1d
        lattice and about 2/3 through the 2d square lattice.
\end{itemize}

\subsection{Codes}
\begin{itemize}
  \item Set up codes to produce dispersion curve for 1d lattice and 2d
        hexagonal lattice.
  \item Also created code to produce dispersion curve for 2d perturbed
        hexagonal lattice and hexagonal ribbon, but requires more testing to
        validate. 
\end{itemize}

\subsection{Proposed chapter structure of final report}
\begin{enumerate}
  \item Introduction
  \item Background
  \item Dispersion relation
  \item Perturbed system
  \item Scattering simulation
  \item Evaluation
  \item Conclusion
  \item Appendix
  \item Bibliography
\end{enumerate}

\section{What to do}
\begin{enumerate}
  \item Complete section on Brillouin zones; then finish off 2d square
        lattice discussion. Also, fix 2d square model image so it shows the
        separate cells with labels. (1 day)
  \item Complete section on 2d hexagonal lattice. (2 days)
  \item Fix any bugs in codes; generate dispersion curve for perturbed lattice
        and locate bandgap. Then discuss in the report. (1 week)
  \item Use perturbed lattice to form hexagonal ribbon and find dispersion
        curve. Then discuss in the report. (3-4 weeks)  
  \item Develop theory and codes to simulate scattering. Then discuss in the
        report. (3-4 weeks)
  \item Evaluate project and write up conclusion.(1 week)
  \item Prepare final project presentation. (1-2 weeks)
\end{enumerate}

\section{Proposed timeline}
Taking into account my other courses as well as coursework deadlines and exams,
I have set up the following rough timeline:
\begin{itemize}
  \item By 22/02, complete 1 and 2.
  \item By early to mid April, complete 3 and 4.
  \item By mid May, complete 5.
  \item By mid June, complete 6 and 7.
\end{itemize}

\section{What else to do (if time permits)}
\begin{enumerate}
  \item Consider other arrangements (e.g. kagome vs hexagon, different shape of
        bends in our semi-infinite lattice)
  \item Consider active metamaterials? (e.g. metamaterials which change their
        shape/elasticity over time?)
\end{enumerate}


